On the effects of partying on next-day sports performance

### 2017-07-07 writing/draft.tex
Updated tables; now all but demeaned rebounds contain p-values instead of std. err.

% m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.513$^{***}$ &  \\    & (0.145) &  \\    & & \\   Party continuous &  & $-$0.181$^{**}$ \\    &  & (0.091) \\    & & \\   Lag changes in posession & 0.0001 & 0.00004 \\    & (0.002) & (0.002) \\    & & \\   Logged travel distance & $-$0.017 & $-$0.014 \\    & (0.026) & (0.026) \\    & & \\   East-west travel direction & $-$0.145 & $-$0.113 \\    & (0.232) & (0.231) \\    & & \\   Number hours rest time & 0.001 & 0.001 \\    & (0.001) & (0.001) \\    & & \\   Time of game during day & 0.005 & 0.004 \\    & (0.013) & (0.013) \\    & & \\   Home team effect & 0.001 & 0.004 \\    & (0.043) & (0.043) \\    & & \\   Logged travel distance * east-west & 0.022 & 0.018 \\    & (0.036) & (0.036) \\    & & \\   Constant & $-$0.048 & $-$0.028 \\    & (0.378) & (0.378) \\    & & \\  \hline \\[-1.8ex]  Observations & 9,823 & 9,823 \\  Log Likelihood & $-$6,800.677 & $-$6,805.100 \\  Akaike Inf. Crit. & 13,619.350 & 13,628.200 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.126$^{*}$ &  \\    & (0.074) &  \\    & & \\   Nightlife (no weekend interaction) &  & $-$0.016 \\    &  & (0.110) \\    & & \\   Bookmaker's odds & 2.638$^{***}$ & 2.583$^{***}$ \\    & (0.163) & (0.165) \\    & & \\   Home-team effect & 0.008 & 0.034 \\    & (0.035) & (0.083) \\    & & \\   Number of rest days & 0.019 & 0.018 \\    & (0.020) & (0.020) \\    & & \\   Logged travel distance & $-$0.002 & $-$0.003 \\    & (0.005) & (0.005) \\    & & \\   Weekend & 0.044 & 0.003 \\    & (0.038) & (0.030) \\    & & \\   Constant & $-$1.344$^{***}$ & $-$1.324$^{***}$ \\    & (0.081) & (0.113) \\    & & \\  \hline \\[-1.8ex]  Observations & 24,734 & 24,033 \\  Log Likelihood & $-$16,946.080 & $-$16,470.850 \\  Akaike Inf. Crit. & 33,906.160 & 32,955.700 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.072 \\    & (0.082) \\    & \\   Lag changes in posession & 0.00001 \\    & (0.002) \\    & \\   Logged travel distance & $-$0.005 \\    & (0.026) \\    & \\   East-west travel direction & $-$0.099 \\    & (0.231) \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & (0.001) \\    & \\   Time of game during day & 0.001 \\    & (0.013) \\    & \\   Home team effect & $-$0.009 \\    & (0.043) \\    & \\   Logged travel distance * east-west & 0.015 \\    & (0.036) \\    & \\   Constant & $-$0.069 \\    & (0.378) \\    & \\  \hline \\[-1.8ex]  Observations & 9,823 \\  Log Likelihood & $-$6,806.701 \\  Akaike Inf. Crit. & 13,631.400 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% m2
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Demeanead Rebounds Per Minute \\  \hline \\[-1.8ex]   Continuous party measure & $-$0.003$^{*}$ \\    & (0.002) \\    & \\   Lag change in possessions & 0.00003 \\    & (0.0001) \\    & \\   Logged travel distance & 0.001 \\    & (0.001) \\    & \\   Number hours since last game & 0.00003 \\    & (0.00002) \\    & \\   Constant & $-$0.008$^{*}$ \\    & (0.004) \\    & \\  \hline \\[-1.8ex]  Observations & 43,547 \\  R$^{2}$ & 0.0003 \\  Adjusted R$^{2}$ & 0.0002 \\  Residual Std. Error & 0.104 (df = 43542) \\  F Statistic & 2.945$^{**}$ (df = 4; 43542) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

\paragraph{The hangover correlates with allowing more points}
Similarly, common knowledge also suggests that the overall defense of a team
is effected strongly by individual player effort. It seems likely that a hangover effect
would be more prevalent on the defensive aspects of gameplay. To that end, we examine points allowed and points scored as a function of exposure to nightlife.
It's worth noting that travel to party cities is correlated with allowing
more points on the subsequent day of gameplay, but the null hypothesis
can't be rejected for points scored.

@@

% mpa1, tpa, tpo
\hspace{-100pt}
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & Points Admitted by Team & Team Points Admitted & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.828$^{***}$ &  &  \\    & (0.699) &  &  \\    & & & \\   Continuous party measure &  & 1.667$^{***}$ & 0.080 \\    &  & (0.587) & (0.575) \\    & & & \\   Lag change in possessions &  & 0.267$^{***}$ & 0.285$^{***}$ \\    &  & (0.016) & (0.016) \\    & & & \\   Logged travel distance &  & $-$0.447$^{**}$ & 0.143 \\    &  & (0.191) & (0.187) \\    & & & \\   Number hours since last game &  & 0.011 & 0.017$^{**}$ \\    &  & (0.007) & (0.007) \\    & & & \\   Constant & $-$0.047 & 70.710$^{***}$ & 64.859$^{***}$ \\    & (0.090) & (2.271) & (2.223) \\    & & & \\  \hline \\[-1.8ex]  Observations & 15,658 & 6,426 & 6,426 \\  R$^{2}$ & 0.001 & 0.045 & 0.051 \\  Adjusted R$^{2}$ & 0.001 & 0.044 & 0.051 \\  Residual Std. Error & 11.159 (df = 15656) & 11.941 (df = 6421) & 11.688 (df = 6421) \\  F Statistic & 16.357$^{***}$ (df = 1; 15656) & 74.877$^{***}$ (df = 4; 6421) & 86.792$^{***}$ (df = 4; 6421) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

\section{Conclusions and Avenues for Future Research}
\subsection{Extending the research}
\paragraph{Within the NBA} 
We're interested to explore what other factors may affect a team's propensity to suffer hangover effects beyond simply visiting a party city; e.g. are teams more likely to go out after
a win or a loss? Do teams who aren't going to make the playoffs party more? Are there demographic
factors which influence partying, e.g. are younger, unmarried players more susceptible to treatment effect? Within a game, it would be interesting to look at 
number of shots taken, and number of shots taken by 
stars as a function of previous day visitation to party cities. We could also investigate 
effects on injury risk and flagrant foul rates.

>>>>

% m0, m1
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Meet the Spread} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Party discrete & $-$0.555$^{***}$ &  \\    & p = 0.0002 &  \\    & & \\   Party continuous &  & $-$0.153 \\    &  & p = 0.107 \\    & & \\   Lag changes in posession & 0.001 & 0.001 \\    & p = 0.346 & p = 0.373 \\    & & \\   Logged travel distance & $-$0.014 & $-$0.009 \\    & p = 0.577 & p = 0.733 \\    & & \\   East-west travel direction & $-$0.074 & $-$0.039 \\    & p = 0.754 & p = 0.867 \\    & & \\   Number hours rest time & 0.001 & 0.001 \\    & p = 0.218 & p = 0.295 \\    & & \\   Time of game during day & 0.007 & 0.005 \\    & p = 0.603 & p = 0.715 \\    & & \\   Home team effect & 0.002 & 0.004 \\    & p = 0.960 & p = 0.936 \\    & & \\   Logged travel distance * east-west & 0.012 & 0.007 \\    & p = 0.749 & p = 0.846 \\    & & \\   Constant & $-$0.247 & $-$0.229 \\    & p = 0.443 & p = 0.477 \\    & & \\  \hline \\[-1.8ex]  Observations & 9,517 & 9,517 \\  Log Likelihood & $-$6,587.456 & $-$6,593.324 \\  Akaike Inf. Crit. & 13,192.910 & 13,204.650 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% m3, m4
\begin{tabular}{@{\extracolsep{5pt}}lcc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{2}{c}{\textit{Dependent variable:}} \\  \cline{2-3}  \\[-1.8ex] & \multicolumn{2}{c}{Probability of Winning} \\  \\[-1.8ex] & (1) & (2)\\  \hline \\[-1.8ex]   Continuous measure of nightlife & $-$0.120$^{*}$ &  \\    & p = 0.091 &  \\    & & \\   Nightlife (no weekend interaction) &  & 0.137 \\    &  & p = 0.307 \\    & & \\   Bookmaker's odds & 2.682$^{***}$ & 2.669$^{***}$ \\    & p = 0.000 & p = 0.000 \\    & & \\   Home-team effect & 0.014 & 0.144 \\    & p = 0.674 & p = 0.159 \\    & & \\   Number of rest days & 0.018 & 0.016 \\    & p = 0.399 & p = 0.456 \\    & & \\   Logged travel distance & $-$0.005 & $-$0.003 \\    & p = 0.377 & p = 0.519 \\    & & \\   Weekend & 0.044 & 0.002 \\    & p = 0.246 & p = 0.935 \\    & & \\   Constant & $-$1.360$^{***}$ & $-$1.468$^{***}$ \\    & p = 0.000 & p = 0.000 \\    & & \\  \hline \\[-1.8ex]  Observations & 26,473 & 26,473 \\  Log Likelihood & $-$18,124.390 & $-$18,125.300 \\  Akaike Inf. Crit. & 36,262.780 & 36,264.600 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.056 \\    & p = 0.504 \\    & \\   Lag changes in posession & 0.001 \\    & p = 0.408 \\    & \\   Logged travel distance & $-$0.003 \\    & p = 0.920 \\    & \\   East-west travel direction & $-$0.036 \\    & p = 0.880 \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & p = 0.098 \\    & \\   Time of game during day & 0.003 \\    & p = 0.827 \\    & \\   Home team effect & $-$0.006 \\    & p = 0.896 \\    & \\   Logged travel distance * east-west & 0.006 \\    & p = 0.866 \\    & \\   Constant & $-$0.257 \\    & p = 0.425 \\    & \\  \hline \\[-1.8ex]  Observations & 9,517 \\  Log Likelihood & $-$6,594.404 \\  Akaike Inf. Crit. & 13,206.810 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

@@

% m2
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Demeanead Rebounds Per Minute \\  \hline \\[-1.8ex]   Continuous party measure & $-$0.004$^{*}$ \\    & (0.002) \\    & \\   Lag change in possessions & 0.00002 \\    & (0.0001) \\    & \\   Logged travel distance & 0.001 \\    & (0.001) \\    & \\   Number hours since last game & 0.00002 \\    & (0.00002) \\    & \\   Constant & $-$0.007 \\    & (0.004) \\    & \\  \hline \\[-1.8ex]  Observations & 40,684 \\  R$^{2}$ & 0.0003 \\  Adjusted R$^{2}$ & 0.0002 \\  Residual Std. Error & 0.104 (df = 40679) \\  F Statistic & 2.696$^{**}$ (df = 4; 40679) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  
\paragraph{The hangover correlates with allowing more points}
Similarly, common knowledge also suggests that the overall defense of a team
is effected strongly by individual player effort. It seems likely that a hangover effect
would be more prevalent on the defensive aspects of gameplay. To that end, we examine points allowed and points scored as a function of exposure to nightlife.
It's worth noting that travel to party cities is correlated with allowing
more points on the subsequent day of gameplay, but the null hypothesis
can't be rejected for points scored.

@@

% mpa1, tpa, tpo
\hspace{-100pt}
\begin{tabular}{@{\extracolsep{5pt}}lccc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{3}{c}{\textit{Dependent variable:}} \\  \cline{2-4}  \\[-1.8ex] & Points Admitted by Team & Team Points Admitted & Team Points Scored \\  \\[-1.8ex] & (1) & (2) & (3)\\  \hline \\[-1.8ex]   Discrete party indicator & 2.817$^{***}$ &  &  \\    & p = 0.0001 &  &  \\    & & & \\   Continuous party measure &  & 1.803$^{***}$ & $-$0.160 \\    &  & p = 0.007 & p = 0.806 \\    & & & \\   Lag change in possessions &  & 0.118$^{***}$ & 0.115$^{***}$ \\    &  & p = 0.000 & p = 0.000 \\    & & & \\   Logged travel distance &  & $-$0.568$^{***}$ & 0.037 \\    &  & p = 0.005 & p = 0.852 \\    & & & \\   Number hours since last game &  & 0.011 & 0.018$^{**}$ \\    &  & p = 0.115 & p = 0.013 \\    & & & \\   Constant & $-$0.046 & 89.567$^{***}$ & 86.136$^{***}$ \\    & p = 0.612 & p = 0.000 & p = 0.000 \\    & & & \\  \hline \\[-1.8ex]  Observations & 15,139 & 6,234 & 6,234 \\  R$^{2}$ & 0.001 & 0.023 & 0.021 \\  Adjusted R$^{2}$ & 0.001 & 0.023 & 0.021 \\  Residual Std. Error & 11.137 (df = 15137) & 12.071 (df = 6229) & 11.910 (df = 6229) \\  F Statistic & 15.670$^{***}$ (df = 1; 15137) & 37.032$^{***}$ (df = 4; 6229) & 33.756$^{***}$ (df = 4; 6229) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  
\section{Conclusions and Avenues for Future Research}
\subsection{Extending the research}
\paragraph{Within the NBA} 
We're interested to explore what other factors may affect a team's propensity to suffer hangover effects beyond simply visiting a party city; e.g. are teams more likely to go out after
a win or a loss? Do teams who aren't going to make the playoffs party more? Are there demographic
factors which influence partying, e.g. are younger, unmarried players more susceptible to treatment effect? Within a game, it would be interesting to look at 
number of shots taken, and number of shots taken by 
stars as a function of previous day visitation to party cities. We could also investigate 
effects on injury risk and flagrant foul rates.
